Technical Report

### 2018-05-31 fully-abstract-comp/technical-report.tex
Fixed permission based stack conditions.
Typos and formatting.

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\begin{align*}
  \sem{\txjmp{r_1}{r_2}}(\Phi) = &
                                   \begin{cases}
                                       \Phi''
                                     &
                                     \begin{array}[t]{l}
                                       \Phi(r_1) = \sealed{\sigma_1,c_1} \tand
                                       \Phi(r_2) = \sealed{\sigma_2,c_2} \tand\\
                                       \sigma_1 = \sigma_2 \tand \\
                                       w_1 = \linCons{c_1} \tand \\
                                       w_2 = \linCons{c_2} \tand \\
                                       \Phi' = \Phi \updReg{r_1}{w_1} \updReg{r_2}{w_2} \tand\\
                                       \Phi'' = \xjumpResult{c_1}{c_2}{\Phi'}
                                     \end{array}\\
                                     \failed & \totherwise
                                   \end{cases}
\end{align*}
\begin{align*}
  \xjumpResult{c_1}{c_2}{\Phi} = 
  \begin{cases}
    \arraycolsep=0pt
    \begin{array}[t]{rl}
      \Phi & \updReg{\pcreg}{c_1}\\
           & \updReg{\rdata}{c_2}
    \end{array} &
    \begin{array}[t]{l}
      c_1 \neq \retptrc(\_) \tand \\
      c_2 \neq \retptrd(\_) \tand \\
      \nonExec{c_\data}
    \end{array}
    \\&\\
    \sourcecolor\left.
      \arraycolsep=0pt
      \begin{array}[t]{rl}
        \Phi' & \updReg{\pcreg}{c_\opc}\\
              & \updReg{\rdata}{0}\\
              & \updReg{\rstk}{c_\stk}\\
              & \updReg{\rtmp{1}}{0}\\
              & \updReg{\rtmp{2}}{0}
      \end{array}\right.&
    \sourcecolor\left.
      \begin{array}[t]{l}
        c_1 = \retptrc(\baddr,\eaddr,\aaddr) \tand \\
        c_2 = \retptrd(\aaddr_\stk,\eaddr_{\stk,\priv}) \tand \\
        \Phi(\rstk) = \stkptr{\rw,\stkb,\eaddr_\stk,\_} \tand \\ 
        \Phi = (\mem,\reg,\stkf::\stk,\ms_\stk) \tand \\
        \stkf = (\opc,\ms_{\stk,\priv}) \tand \\
        \opc = \aaddr \tand \\
        c_\opc = ((\rx,\normal),\baddr,\eaddr,\opc) \tand \\
        \dom(\ms_{\stk,\priv}) = [\eaddr_\stk+1,\eaddr_{\stk,\priv}] \tand\\
        e_\stk + 1 = a_\stk \tand\\
        c_\stk = \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},\aaddr_\stk} \tand\\
        \Phi' = (\mem,\reg,\stk,\ms_{\stk,\priv} \uplus \ms_\stk) 
      \end{array}\right.
    \\
    \failed & \totherwise
  \end{cases}
\end{align*}

@@

We define a component as follows:
\begin{align*}
  \var{comp}_0 &\mathrel{::=} (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)\\
  \var{comp} &\mathrel{::=} \var{comp}_0\\
               &\mid  (\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})
\end{align*}

We define inductively when a component is valid ($\vdash \var{comp}$) by the below inference rules:
\begin{mathpar}
  \inference{
    \mscode(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr} & [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets \cup \sigcloss)
  }{
    \sigrets,\sigrets[\mathrm{owned}],\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \mscode(a) \in \ints\\
    \mscode([a \cdots a + \calllen-1]) = \scall[0..\calllen-1]{\offpc,\offsigma}{r_1}{r_2} \Rightarrow (\mscode(a+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr} \wedge \sigma_\baddr+\offsigma \in \sigrets[\mathrm{owned}])
  }{
    \sigrets,\sigrets[\mathrm{owned}],\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \exists d_\sigma : \dom(\mscode) \rightarrow \powerset{\Seal} \ldotp
    \sigrets = \biguplus_{a \in \dom(\mscode)} d_\sigma(a) \tand\\
    \forall a \in \dom(\mscode) \ldotp 
    \sigrets,d_\sigma(a),\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode
  }
  \and
  \inference{
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & 
    \sigma \in \sigcloss
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \sealed{\sigma,((\rx,\normal),\baddr,\eaddr,\aaddr)}
  }
  \and
  \inference{
    \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}} &
    \lin = \normal \Rightarrow [\baddr,\eaddr] \subseteq A_{\mathrm{non-linear}}
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \vsc \\
    \sigma \in \sigcloss
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \sealed{\sigma,\vsc}
  }
  \and
  \inference{
    \dom(\mscode) \mathrel{\#} \dom(\msdata)\\
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode \\
    \exists A_\mathrm{own} : \dom(\msdata) \rightarrow \powerset{\dom(\msdata)} & \dom(\msdata) = A_{\mathrm{non-linear}} \uplus \biguplus_{a \in \dom(\msdata)} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\msdata)\ldotp \dom(\mscode),A_{\mathrm{own}}(a),A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \msdata(a)\\
    \overline{\dom(\mscode), \emptyset, A_{\mathrm{non-linear}}, \overline{c_{\mathrm{import}}}, \sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c_{\mathrm{export}}}\\
    \overline{c_{\mathrm{export}}} \mathrel{\#} \overline{c_{\mathrm{import}}}
  }{
    \vdash (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  }
  \and
  \inference{
    \var{comp}_0 = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)\\
    \vdash \var{comp}_0 & c_{\mathrm{main},c}, c_{\mathrm{main},d} \in \overline{c_{\mathrm{export}}}
  }{
    \vdash (\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})
  }
\end{mathpar}

@@

\[
  \readCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad \lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1\\
      \qquad \quad \forall r \in S \ldotp \pwheap(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \quad \forall r \in S \ldotp \pwfree(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists M : S \fun \powerset{\MemSeg} \\
      \qquad \biguplus_{r\in S} \dom(M(r)) \supseteq A \wedge\\
      \qquad \lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1\\
      % \qquad \biguplus_{r\in S} R(r) \# \biguplus_{r\in S} C(r) \wedge \\
      \qquad \quad \forall r \in S \ldotp  \pwheap(r) \nequal \codereg{\_,\_,M(r),\gc}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions.}
\lau{TODO: allow code regions to be merged into one. Allow for (... forgot to write the rest, but probably related to splicing regions.) }

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad \lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1\\
      \qquad \quad \forall r \in S \ldotp \pwheap(r) \nsupeq \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether necessary for the stack region.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
% \dominique{Why $n-1$ above?  There is already a quantification over $n' <n$ in the memory satisfaction relation and another $n-1$ is used in $\stdreg{[\baddr',\eaddr'],\gc}{\pur}$. Also: readCond doesn't have the $n-1$. Update: the memory satisfaction was updated by Lau to remove the quantification over $n' < n$ and I dropped the $n-1$ here.}
\[
  \stackWriteCond{W} = \left\{ \npair{[\baddr,\eaddr]}) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr] \wedge \\
      \qquad \quad \forall r \in S \ldotp \pwfree(r) \nsupeq \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwfree(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

>>>>

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\begin{align*}
  \sem{\txjmp{r_1}{r_2}}(\Phi) = &
                                   \begin{cases}
                                       \Phi''
                                     &
                                     \begin{array}[t]{l}
                                       \Phi(r_1) = \sealed{\sigma_1,c_1} \tand
                                       \Phi(r_2) = \sealed{\sigma_2,c_2} \tand\\
                                       \sigma_1 = \sigma_2 \tand \\
                                       w_1 = \linCons{c_1} \tand \\
                                       w_2 = \linCons{c_2} \tand \\
                                       \Phi' = \Phi \updReg{r_1}{w_1} \updReg{r_2}{w_2} \tand\\
                                       \Phi'' = \xjumpResult{c_1}{c_2}{\Phi'}
                                     \end{array}\\
                                     \failed & \totherwise
                                   \end{cases}
\end{align*}
\begin{align*}
  \xjumpResult{c_1}{c_2}{\Phi} = 
  \begin{cases}
    \arraycolsep=0pt
    \begin{array}[t]{rl}
      \Phi & \updReg{\pcreg}{c_1}\\
           & \updReg{\rdata}{c_2}
    \end{array} &
    \begin{array}[t]{l}
      c_1 \neq \retptrc(\_) \tand \\
      c_2 \neq \retptrd(\_) \tand \\
      \nonExec{c_2}
    \end{array}
    \\&\\
    \sourcecolor\left.
      \arraycolsep=0pt
      \begin{array}[t]{rl}
        \Phi' & \updReg{\pcreg}{c_\opc}\\
              & \updReg{\rdata}{0}\\
              & \updReg{\rstk}{c_\stk}\\
              & \updReg{\rtmp{1}}{0}\\
              & \updReg{\rtmp{2}}{0}
      \end{array}\right.&
    \sourcecolor\left.
      \begin{array}[t]{l}
        c_1 = \retptrc(\baddr,\eaddr,\aaddr) \tand \\
        c_2 = \retptrd(\aaddr_\stk,\eaddr_{\stk,\priv}) \tand \\
        \Phi(\rstk) = \stkptr{\rw,\stkb,\eaddr_\stk,\_} \tand \\ 
        \Phi = (\mem,\reg,\stkf::\stk,\ms_\stk) \tand \\
        \stkf = (\opc,\ms_{\stk,\priv}) \tand \\
        \opc = \aaddr \tand \\
        c_\opc = ((\rx,\normal),\baddr,\eaddr,\opc) \tand \\
        \dom(\ms_{\stk,\priv}) = [\eaddr_\stk+1,\eaddr_{\stk,\priv}] \tand\\
        e_\stk + 1 = a_\stk \tand\\
        c_\stk = \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},\aaddr_\stk} \tand\\
        \Phi' = (\mem,\reg,\stk,\ms_{\stk,\priv} \uplus \ms_\stk) 
      \end{array}\right.
    \\
    \failed & \totherwise
  \end{cases}
\end{align*}

@@

We define a component as follows:
  \var{comp}_0 &\mathrel{::=} (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)\\
  \var{comp} &\mathrel{::=} \var{comp}_0\\
               &\mid  (\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})
\clearpage
We define inductively when a component is valid ($\vdash \var{comp}$) by the below inference rules:
\begin{mathpar}
  \inference{
    \mscode(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr} & [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets \cup \sigcloss)
  }{
    \sigrets,\sigrets[\mathrm{owned}],\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \mscode(a) \in \ints\\
    \mscode([a \cdots a + \calllen-1]) = \scall[0..\calllen-1]{\offpc,\offsigma}{r_1}{r_2} \Rightarrow (\mscode(a+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr} \wedge \sigma_\baddr+\offsigma \in \sigrets[\mathrm{owned}])
  }{
    \sigrets,\sigrets[\mathrm{owned}],\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \exists d_\sigma : \dom(\mscode) \rightarrow \powerset{\Seal} \ldotp
    \sigrets = \biguplus_{a \in \dom(\mscode)} d_\sigma(a) \tand\\
    \forall a \in \dom(\mscode) \ldotp 
    \sigrets,d_\sigma(a),\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode
  }
  \and
  \inference{
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & 
    \sigma \in \sigcloss
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \sealed{\sigma,((\rx,\normal),\baddr,\eaddr,\aaddr)}
  }
  \and
  \inference{
    \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}} &
    \lin = \normal \Rightarrow [\baddr,\eaddr] \subseteq A_{\mathrm{non-linear}}
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \vsc \\
    \sigma \in \sigcloss
  }{
    A_{\mathrm{code}},A_{\mathrm{own}},A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \sealed{\sigma,\vsc}
  }
  \and
  \inference{
    \dom(\mscode) \mathrel{\#} \dom(\msdata)\\
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode \\
    \exists A_\mathrm{own} : \dom(\msdata) \rightarrow \powerset{\dom(\msdata)} & \dom(\msdata) = A_{\mathrm{non-linear}} \uplus \biguplus_{a \in \dom(\msdata)} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\msdata)\ldotp \dom(\mscode),A_{\mathrm{own}}(a),A_{\mathrm{non-linear}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \msdata(a)\\
    \overline{\dom(\mscode), \emptyset, A_{\mathrm{non-linear}}, \overline{c_{\mathrm{import}}}, \sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c_{\mathrm{export}}}\\
    \overline{c_{\mathrm{export}}} \mathrel{\#} \overline{c_{\mathrm{import}}}
  }{
    \vdash (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  }
  \and
  \inference{
    \var{comp}_0 = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)\\
    \vdash \var{comp}_0 & c_{\mathrm{main},c}, c_{\mathrm{main},d} \in \overline{c_{\mathrm{export}}}
  }{
    \vdash (\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})
  }
\end{mathpar}

@@

\[
  \readCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      \qquad \forall r \in S \ldotp \pwheap(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \forall r \in S \ldotp |R(r)| = 1\\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \forall r \in S \ldotp \pwfree(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists M : S \fun \powerset{\MemSeg} \\
      \qquad \biguplus_{r\in S} \dom(M(r)) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      % \qquad \biguplus_{r\in S} R(r) \# \biguplus_{r\in S} C(r) \wedge \\
      \qquad \forall r \in S \ldotp  \pwheap(r) \nequal \codereg{\_,\_,M(r),\gc}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions.}
\lau{TODO: allow code regions to be merged into one. Allow for (... forgot to write the rest, but probably related to splicing regions.) }

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      \qquad \forall r \in S \ldotp \pwheap(r) \nsupeq \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether necessary for the stack region.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
% \dominique{Why $n-1$ above?  There is already a quantification over $n' <n$ in the memory satisfaction relation and another $n-1$ is used in $\stdreg{[\baddr',\eaddr'],\gc}{\pur}$. Also: readCond doesn't have the $n-1$. Update: the memory satisfaction was updated by Lau to remove the quantification over $n' < n$ and I dropped the $n-1$ here.}
\[
  \stackWriteCond{W} = \left\{ \npair{A}) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \forall r \in S \ldotp |R(r)| = 1 \wedge \\
      \qquad \forall r \in S \ldotp \pwfree(r) \nsupeq \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwfree(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
